Metrics

### 2025-02-23 manuscript/manuscript.tex
Rearrange src code

\author[1]{\fnm{Cheryl} \sur{Chin}}\email{cheryl.chin@unityhealth.to}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agegroup.pdf}
\caption{Model performance by age group for assigning CGHR-10 CODs.}\label{fig-perf-agegroup}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-cod-child.pdf}
\caption{Model performance for child records by CGHR-10 COD.}\label{fig-perf-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-cod-neo.pdf}
\caption{Model performance for neonatal records by COD. GPT-3.5, GPT-4, InterVA-5, and InSilicoVA model performance for assigning CGHR-10 CODs in the neonatal age group (under 28 years) by COD. PCCC values are sorted by the highest to lowest PCCC for each COD. Only models with PCCC values within .05 of the highest and lowest PCCC are shown. Congenital anomalies and other are not notable due to small sample sizes of 2 and 5 respectively.}\label{fig-perf-cod-neo}
\end{figure}

@@

Another research opportunity is in the integration of GPT, InterVA-5, and InSilicoVA models into VA systems to assist physicians in COD assignment. In dual-coded VA systems (described in Section \ref{methods-data}), two physicians are randomly assigned to each record and require second inspections of each other's assignment (reconciliation) and evaluation by a third more senior physician if their assignments do not agree. As mentioned in Section \ref{discuss-adv-hscav}, suggestion of alternative assignments from GPT and InSilicoVA models potentially reduces the disagreement between physicians, and ill-defined records, while allowing physicians to focus on more difficult records. Thus, model suggestions can be integrated into VA systems by presenting model suggestions to physicians after their initial COD assignment, which allows them to consider alternative assignments and possibly revise their assignments based on the suggestions (Figure \ref{fig-discuss-phyassist}). Our future work will be a first step in computer assisted verbal autopsy, assessing the effects of these model suggestions on physician assignment outcomes (e.g. increase in agreed records, reduction of ill-defined deaths). In preparation, we have integrated GPT-4, InterVA-5, and InSilicoVA model suggestions into our HEAL-SL study for after survey round 2 \citep{njalauniversityHealthySierraLeone2023}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{fig-discuss-phyassist.pdf}
    \caption{Addition of model suggestions into the physician assignment process. At step 2, GPT, InterVA-5, and InSilicoVA models can suggest COD assignments to consider, providing the option in step 2b to revise or proceed with their initial assignment. The additional consideration potentially reduces disagreement between physicians and ill-defined deaths.}\label{fig-discuss-phyassist}
\end{figure}

@@

\section{Case Study Data Exploration}\label{app-data}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-sampling.pdf}
\caption{HEAL-SL sampling areas and VA records with physician assigned CODs only from 2019-2022.}\label{fig-data-sampling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agesex.pdf}
\caption{Number of physician agreed VA records by age groups in Sierra Leone from 2019 to 2022.}\label{fig-data-agesex}
\end{figure}

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange.pdf}
\caption{Number of physician agreed VA records by 5-year age ranges in Sierra Leone from 2019 to 2022.}\label{fig-data-agerange}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange-adult.pdf}
\caption{Number of physician agreed adult (12 to 69 years) VA records by 5-year age ranges in Sierra Leone from 2019 to 2022.}\label{fig-data-agerange-adult}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-cod-adult.pdf}
\caption{Number of physician agreed adult (12 to 69 years) VA records by CGHR-10 COD code in Sierra Leone from 2019 to 2022.}\label{fig-data-cod-adult}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange-child.pdf}
\caption{Number of physician agreed child (28 days to 11 years) VA records by 5-year age ranges in Sierra Leone from 2019 to 2022.}\label{fig-data-agerange-child}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-cod-child.pdf}
\caption{Number of physician agreed child (28 days to 11 years) VA records by CGHR-10 COD code in Sierra Leone from 2019 to 2022.}\label{fig-data-cod-child}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange-neo.pdf}
\caption{Number of physician agreed neonatal (less than 28 days) VA records by 5-year age ranges in Sierra Leone from 2019 to 2022.}\label{fig-data-agerange-neo}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-cod-neo.pdf}
\caption{Number of physician agreed neonatal (less than 28 days) VA records by CGHR-10 COD code in Sierra Leone from 2019 to 2022.}\label{fig-data-cod-neo}
\end{figure}

\section{Case Study Methods}\label{app-methods}

>>>>

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agegroup.pdf}
\caption{Model performance by age group.}\label{fig-perf-agegroup}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-cod-child.pdf}
\caption{Model performance for child records by COD.}\label{fig-perf-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-cod-neo.pdf}
\caption{Model performance for neonatal records by COD.}\label{fig-perf-cod-neo}
\end{figure}

@@

Another research opportunity is in the integration of GPT, InterVA-5, and InSilicoVA models into VA systems to assist physicians in COD assignment. In dual-coded VA systems (described in Section \ref{methods-data}), two physicians are randomly assigned to each record and require second inspections of each other's assignment (reconciliation) and evaluation by a third more senior physician if their assignments do not agree. As mentioned in Section \ref{discuss-adv-hscav}, suggestion of alternative assignments from GPT and InSilicoVA models potentially reduces the disagreement between physicians, and ill-defined records, while allowing physicians to focus on more difficult records. Thus, model suggestions can be integrated into VA systems by presenting COD suggestions to physicians after their initial COD assignment, which allows them to consider alternative assignments and possibly revise their assignments based on the suggestions. At step 2 in Figure \ref{fig-discuss-phyassist}, GPT, InterVA-5, and InSilicoVA models can suggest COD assignments to consider, providing the option in step 2b to revise or proceed with their initial assignment. Our future work will be a first step in computer assisted verbal autopsy, assessing the effects of these model suggestions on improve VA data quality (e.g. increase in agreed records, reduction of ill-defined deaths). In preparation, we have integrated GPT-4, InterVA-5, and InSilicoVA model suggestions into our HEAL-SL study after survey round 2 \citep{njalauniversityHealthySierraLeone2023}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{fig-discuss-phyassist.pdf}
    \caption{Model suggestions integrated in the physician assignment process.}\label{fig-discuss-phyassist}
\end{figure}

@@

\section{Data Exploration}\label{app-data}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-sampling.pdf}
\caption{Case study data sampling areas.}\label{fig-data-sampling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agesex.pdf}
\caption{All records by age group and five-year age range.}\label{fig-data-agesex}
\end{figure}

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange.pdf}
\caption{All records by five-year age range.}\label{fig-data-agerange}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange-adult.pdf}
\caption{Adult records by five-year age range.}\label{fig-data-agerange-adult}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-cod-adult.pdf}
\caption{Adult records by COD.}\label{fig-data-cod-adult}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange-child.pdf}
\caption{Child records by five-year age range.}\label{fig-data-agerange-child}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-cod-child.pdf}
\caption{Child records by COD.}\label{fig-data-cod-child}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-agerange-neo.pdf}
\caption{Neonatal records by five-year age range.}\label{fig-data-agerange-neo}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-data-cod-neo.pdf}
\caption{Neonatal records by COD.}\label{fig-data-cod-neo}
\end{figure}

\section{Details on Methods}\label{app-methods}

### 2025-02-23 src/plots.Rmd
Working on discussion
Rearrange src code

Calculate Partial Chance Corrected Concordance (PCCC) to evaluate indivudal performance for each model by age and physician coding stage.

@@

>>>>

Calculate Partial Chance Corrected Concordance (PCCC) to evaluate individual performance for each model by age and physician coding stage.

@@

#### COD Sensitivty and Specificity

Create heat map of sensitivity and specificity for each cause of death by model.

```{r}
```
